--- 
title: "Automatic Sampling and Analysis of YouTube Data"
subtitle: "Tools for the Automatic Sampling of YouTube Data"
author: "Julian Kohne<br />Johannes Breuer<br />M. Rohangis Mohseni"
date: "2020-02-24"
location: "GESIS, Cologne, Germany"
output:
  bookdown::pdf_document2
  xaringan::moon_reader:
    lib_dir: libs
    css: ["default", "default-fonts", "../workshop.css"]
    nature:
      highlightStyle: "github"
      highlightLines: true
      countIncrementalSlides: false
---

layout: true

```{r setup, include = F}
if (!require(easypackages)) install.packages("easypackages")
library(easypackages)

packages("knitr", "rmarkdown", "tidyverse", "kableExtra", "hadley/emo", prompt = F)

options(htmltools.dir.version = FALSE)

opts_chunk$set(echo = FALSE, fig.align = "center")

```

<div class="my-footer">
  <div style="float: left;"><span>`r gsub("<br />", ", ", gsub("<br /><br />|<a.+$", "", metadata$author))`</span></div>
  <div style="float: right;"><span>`r metadata$location`, `r metadata$date`</span></div>
  <div style="text-align: center;"><span>`r gsub(".+<br />", " ", metadata$subtitle)`</span></div>
</div>

<style type="text/css">

pre {
  font-size: 10px
}
</style>

---

# Tools for the Automatic Sampling of YouTube Data

- [Webometric Analyst](http://lexiurl.wlv.ac.uk/)

- [YouTube Data Tools](https://tools.digitalmethods.net/netvizz/youtube/)

- [tuber](https://cran.r-project.org/web/packages/tuber/)

We wrote a [short tutorial](https://github.com/gesiscss/YouTubeComments/blob/master/How%20to%20automatically%20sample%20comments%20from%20YouTube_v3.pdf) on how to use the tools. **NB**: The `tuber` script mentioned in that tutorial is a bit outdated. We will explore how to work with `tuber` in more detail in this workshop.

---

# Pros and Cons

```{r tools table 2, echo = F}
tools_pc <- data.frame(
  "Method" = c("Need API Key?", "Disadvantages", "Ease of Use", "License", "Example: Dayum Video (22-02-2019, 2pm)"),
  "Manual Coding" = c("No", "Time-consuming", "High", "n/a", "47,163"),
  "Webometric Analyst" = c("Yes", "Only first 5 follow-up comments, no error feedback, undetectable time-outs", "Low", "Free for n/c", "44,828"),
  "YouTube Data Tools" = c("No", "Lacking flexibility, fewer infos", "High", "Open Source", "47,153"),
  "tuber" = c("Yes", "Only first 5 follow-up comments due to bug", "Low", "Open Source", "44,810")
  , stringsAsFactors = FALSE
  , check.names = FALSE
)
knitr::kable(
  tools_pc
  , format = "html"
  , align = "cc"
  , escape = FALSE
)
```

[Dayum Video](https://www.youtube.com/watch?v=DcJFdCmN98s) / [tuber bug](https://github.com/soodoku/tuber/issues/52)

---

class: center, middle

# Any questions?